Estimating Carrying Capacity for Chinook Parr using Quantile Random Forest Models

### 2020-06-10 analysis/paper/paper.Rmd
added cite keys to Biological Expectations section

The results of the QRF parr capacity model for spring/summer Chinook salmon meet many biological expectations. Focusing on the partial dependence plots (Figure \@ref(fig:pdp-figure)), the QRF model predicts capacity to increase when the wetted width, discharge and the width-to-depth ratio grow, when temperatures are cooler, when there is less fine sediment, when there is more fish cover, when channel unit frequency increases and when the standard deviation of the wetted depth (a proxy for streambed complexity) increases. These are all patterns that emerged from the fish-habitat data, and where available, match those fish-habitat relationships identified qualitatively in other studies [@Mossop2006].

@@

<!-- Try to include images of high capacity / low capacity sites  -->
See Figures \@ref(fig:site-photo-high) and \@ref(fig:site-photo-low).

>>>>

The results of the QRF parr capacity model for spring/summer Chinook salmon meet many biological expectations. Focusing on the partial dependence plots (Figure \@ref(fig:pdp-figure)), the QRF model predicts capacity to increase when the wetted width, discharge and the width-to-depth ratio grow, when temperatures are cooler [@Bjornn1991; @Raleigh1986; @Brett1952], when there is less fine sediment [@Allen2000; @Bjornn1991; @Hillman1987], when there is more fish cover [@Holecek2009; @Bjornn1991; @Hillman1987], when channel unit frequency increases and when the standard deviation of the wetted depth (a proxy for streambed complexity) increases. These are all patterns that emerged from the fish-habitat data, and where available, match those fish-habitat relationships identified qualitatively in other studies [@Mossop2006].

@@
